The \project{unRAVE} catalog

### 2016-09-05 article/unrave.tex
no more conclusion

We briefly describe the \rave\ data in Section~\ref{sec:data}, before explaining
our methods in Section~\ref{sec:method}.  In Section~\ref{sec:validation}
we outline a number of validation experiments, including: internal sanity checks,
comparisons with literature samples, and investigations to ensure our results
are consistent with expectations from astrophysics.  We discuss the implications
of these comparisons and our results in Section~\ref{sec:discussion}.  We provide
concluding remarks in Section~\ref{sec:conclusion}, and describe how to access our
results electronically.

>>>>

We briefly describe the \rave\ data in Section~\ref{sec:data}, before explaining
our methods in Section~\ref{sec:method}.  In Section~\ref{sec:validation}
we outline a number of validation experiments, including: internal sanity checks,
comparisons with literature samples, and investigations to ensure our results
are consistent with expectations from astrophysics.  We discuss the implications
of these comparisons in Section~\ref{sec:discussion}, and conclude with instructions
for how to access our results electronically.
